---
title: "rodent_ecoregion"
author: "Tao Huang"
date: "August 15, 2019"
output: html_document
---

#load the package
```{r}
library("foreign")
```

#read THE imputed and pantheria table, then merge them
```{r}
imputed<-read.csv("C:/Users/huangt/Downloads/imputedwithpeakwithmeanwithmeanenv.csv",header=T)
pantheria<-read.csv("C:/Users/huangt/Documents/MammalEcoregion/2019/upload/PanTHERIA_1-0_WR05_Aug2008.csv",header=T
                    #,sep="\t"
                    )
pantheria$MSW05_Binomial<-gsub(" ","_",pantheria$MSW05_Binomial)
PanTHERIA_IUCN_translation_Rodentia_Soricomorpha<-read.csv("C:/Users/huangt/Documents/PanTHERIA_IUCN_translation_Rodentia_Soricomorpha.csv")

PanTHERIA_IUCN_translation_Rodentia_Soricomorpha$MSW05_Binomial<-gsub(" ","_",PanTHERIA_IUCN_translation_Rodentia_Soricomorpha$MSW05_Binomial)

imputed_IUCN<-merge(imputed,PanTHERIA_IUCN_translation_Rodentia_Soricomorpha,by.x= "species",by.y="MSW05_Binomial")
dim(imputed)
dim(imputed[imputed$species%in%pantheria$MSW05_Binomial ,])
dim(imputed_IUCN)
as.data.frame(table(imputed_IUCN$IUCN_binomial))
#82 species don't have IUCN ranges
write.csv(imputed_IUCN[,c("species","IUCN_binomial")],file="C:/Users/huangt/Documents/imputed_IUCN.csv")
```

#C:\Users\huangt\Documents\bat_virus\TERRESTRIAL_MAMMALS_201907
#join in arcgis
#C:\Users\huangt\Documents\imputed_IUCN_D.shp DISSOLVED BY COL SPECIES
#CREATE AN ECOREGION MATRIX
```{r}
eco_matrix<-read.dbf("C:/Users/huangt/Documents/MammalEcoregion/table/tnc_terr_ecoregions.dbf")

l<-length(eco_matrix$ECO_NAME)
matrix(l,l)

d<-diag(x = 1, 
     #nrow
    l, 
     #ncol
     l, 
     names = TRUE)
d
rownames(d)<-eco_matrix$ECO_NAME
colnames(d)<-eco_matrix$ECO_NAME
write.csv(d,file="C:/Users/huangt/Documents/d.csv")
```
#matrix for $WWF_MHTNAM
# ```{r}
# 
# l2<-length(unique(eco_matrix$WWF_MHTNAM) )
# matrix(l2,l2)
# 
# d2<-diag(x = 1,
#     l2, 
#      l2, 
#      names = TRUE)
# d2
# rownames(d2)<-unique(eco_matrix$WWF_MHTNAM)
# colnames(d2)<-unique(eco_matrix$WWF_MHTNAM)
# write.csv(d2,file="C:/Users/huangt/Documents/d2.csv")
# ```


```{r}
eco_rod<-read.dbf("C:/Users/huangt/Documents/eco_w_rod.dbf")

eco_rod$ID2<-paste("e",eco_rod$ID,sep="")

l<-length(eco_rod$ID2)

d2<-diag(x = 1, 
    l,      l, names = TRUE)
rownames(d2)<-eco_rod$ID2
colnames(d2)<-eco_rod$ID2
d2<-as.data.frame(d2)
#THE ORIGINAL NAMES
d2$ID2<-eco_rod$ID
write.csv(d2,file="C:/Users/huangt/Documents/d4.csv")
```

#matrix for $WWF_MHTNAM
```{r}
#read ecoregion shp dissolved by the col WWF_MHTNAM
WWF_MHTNAM<-read.dbf("C:/Users/huangt/Documents/WWF_MHTNAM.dbf")

WWF_MHTNAM$WWF_ID <-paste("W",WWF_MHTNAM$WWF_ID ,sep="")

l<-length(WWF_MHTNAM$WWF_ID )

d6<-diag(x = 1, 
    l, 
     l, 
     names = TRUE)
rownames(d6)<-WWF_MHTNAM$WWF_ID
colnames(d6)<-WWF_MHTNAM$WWF_ID
d6<-as.data.frame(d6)
d6$ID2<- WWF_MHTNAM$WWF_MHTNAM 
write.csv(d6,file="C:/Users/huangt/Documents/d6.csv")
```

#realm matrix
```{r}
realm<-read.dbf("C:/Users/huangt/Documents/tnc_realm.dbf")
l<-length(realm$WWF_REALM)
d9<-diag(x = 1, l, l, names = TRUE)
rownames(d9)<-realm$WWF_REALM
colnames(d9)<-realm$WWF_REALM
d9<-as.data.frame(d9)

d9$ID2<- unique(eco_matrix$WWF_REALM2)
write.csv(d9,file="C:/Users/huangt/Documents/d9.csv")
```

#fix column names
```{r}
rod_eco<-read.dbf("C:/Users/huangt/Documents/rod_eco.dbf")
colnames(rod_eco)<-c("FID_1","species","Count_","Sum_ECO_ID","Sum_ECO_NU","Sum_CLS_CO","Sum_WWF_MH","Sum_ID",as.character(eco_rod$ECO_NAME),"ID2")
colnames(rod_eco)
rod_eco<-rod_eco[,c(2,9:801)]
colnames(rod_eco)
```

#C:\Users\huangt\Documents\rod_WWF.shp
```{r}
rod_WWF<-read.dbf("C:/Users/huangt/Documents/rod_WWF.dbf")
colnames(rod_WWF)<-c("FID_1","species","Count_","Sum_WWF_ID",as.character(WWF_MHTNAM$WWF_MHTNAM) )
colnames(rod_WWF)

```

#C:\Users\huangt\Documents\imputed_realm.shp
```{r}
imputed_realm<-read.dbf("C:/Users/huangt/Documents/imputed_realm.dbf")
colnames(imputed_realm)
colnames(imputed_realm)<-c("FID_1",   "species", "Count_",as.character(unique(eco_matrix$WWF_REALM2)))
colnames(imputed_realm)
```

#merge imputed rodents with ECOZONE
```{r}
imputed_ecozone<-merge(imputed_IUCN,imputed_realm,by.x="species",by.y= "species",all=T )
write.csv(imputed_ecozone,file="C:/Users/huangt/Documents/imputed_ecozone.csv")
```

#merge imputed rodents with WWF
```{r}
imputed_rod_WWF<-merge(imputed_IUCN,rod_WWF,by.x="species",by.y= "species",all=T )
write.csv(imputed_rod_WWF,file="C:/Users/huangt/Documents/imputed_rod_WWF.csv")
```

#C:\Users\huangt\Documents\rodent_eco.shp
```{r}
rodent_eco<-read.dbf("C:/Users/huangt/Documents/rodent_eco.dbf")
head(rodent_eco)
```
